---
title: "War by the neighbor through the lenses of Hungarian news outlets"
author: "Adam Jozsef Kovacs"
date: "5/11/2022"
output: html_document
---

```{r set chunk options, include=FALSE}
#setting chunk options
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE)
```

## Introduction 

Since Russian troops entered the territory of Ukraine and consequently started a war on the 24th February, 2022, thousands of civilians lost their lives and millions were forced to flee the country. The goal of this blogpost is to grasp interesting patterns in the coverage of the war through an in-depth quantitative text analysis of all articles written on the matter by four pro-government Hungarian news portals. To this end, using web scraping, the texts of more than 2000 articles were collected. 

The main research question of the project is what the communication of these mediums looked like before and after April 3rd 2022, when the Hungarian elections were held and around which time the news about the Bucha massacre became public. My impression dictates the main hypothesis of the post, which is that there has been a change in the coverage. I feel that it focuses much less on the humanitarian aid, and how the Hungarians are pacifists and much more on the painful consequences and how we have to be cautious with breaking all ties with the Russians as we are so dependent on their oil and gas. 

All artifacts of this project including the R script used for scraping the articles can be found in [THIS](https://github.com/kovaad/DS3_project) github repository while the data is uploaded in [THIS](https://drive.google.com/drive/folders/1cMQixfuBkXMLztMrB60vyCPrYCxUBCO3?usp=sharing) Google Drive folder as it was too large to put on github. After downloading it, please put it in the data folder to make the code reproducible.

```{r read in, echo = FALSE}
#clear environment
#rm(list = ls())

#load packages
if (!require("pacman")) {
  install.packages("pacman")
}
pacman::p_load(dplyr,tidyverse, lubridate, tidytext, ggplot2, mediumr,quanteda, pbapply)# quanteda.textstats, ggrepel,text2vec, topicmodels,ggfortify,ggwordcloud)

#check out custom theme
source("theme_adam.R")
```

## Data collection and descriptives

For the data collection, I decided to scrape not only one, but four news outlets coverage on the war. During this process, I first scraped all the titles, the dates (day-month-year) on which the articles were written (this had to be standardized) and the links. Then I went through all these links and scraped the actual content (body) of the articles and merged it back to the dataframe. 

After binding together all the articles, I read it in for the analysis. Then I create an additional dummy variable that signals whether the article was written before or after 3rd April, 2022. For the justification of this date as a milestone refer back to the introduction. 

```{r initial cleaning, echo=FALSE}

#read in data
df <- read_csv("../data/full_df_correct.csv")

#create target variable of before and after the elections
#rename body for text
#remove any unnecessary whitespces
df <- df |> 
  mutate(
    label = ifelse(dates < ymd("2022-4-3"), "before", "after") 
  ) |> 
  rename(text = body)

```

Next, I tokenize all the articles and calculate how many tokens each article consists of. I append this information back to the main dataframe and remove all articles that have less than 10 tokens as they are very unlikely to contain any interesting results to my analysis. 

```{r tokenize and count, echo=FALSE}
#create tidy tokens dataframe using tidytext
tokens <- df |> 
  unnest_tokens(word, text)

#count tokens by article
tok_count <- tokens |> 
  group_by(dates,links) |> 
  summarise( 
    sum_tokens = n()
  )

#add to dataframe this information
df <- left_join(df, tok_count[, names(tok_count) != "dates"], by = "links")

#remove those that contain less than 10 words
df <- subset(df, !(sum_tokens <= 10))

```

The first descriptive plot depicts the number of articles by news portal. As we can see the majority of the articles are from [magyar nemzet](https://magyarnemzet.hu), namely 1348. In their case, these are all the articles with the tag #warinukraine in Hungarian. This is followed by [mandiner](https://mandiner.hu) with 537 articles, where the tag was #Russian-Ukranianwar in Hungarian. The third source is [szoljon](https://www.szoljon.hu), which is the regional news portal for Jász-Nagykun-Szolnok county. It is well-known that all the regional news portal are owned by the same pro-government consortium, so it was chosen to represent that segment of the media. In their case all the articles with the tag #ukraine were pulled from around the start of the Russian invasion. Finally, the fourth news portal is [pesti sracok](https://pestisracok.hu), which is also a pro-government, more radical news portal, where again all articles with the tag #ukraine were collected. 

```{r portal count, include = FALSE}
#create chart of number of articles by news portal
count_by_portal <- df |> group_by(name) |> summarise(count = n()) |> arrange(desc(count))

ggplot(count_by_portal, aes(reorder(name,-count), count)) +
  geom_bar(stat = "identity") +
  labs(
    y = "Number of articles",
    x = NULL
  ) +
  geom_text(data=count_by_portal,aes(label=count,y=count),vjust=-0.5) +
  theme_adam()

ggsave("../images/count_by_portal.png")

```

Next, I was also curious about the time dimension of my data, both the number of articles that were written on these portals and the length of them. First, I visualize the number of articles appeared. The date of appearence of the articles in the data range from 24th January to 1st May (the date of scraping). As we can see on the figure, there are very few articles before the start of war. This is attributable to the fact that, as described earlier, for the two portals with the most articles in the data, the tags searched for when scraping concerned the war specifically so it is logical that it does not have articles before the invasion. For the other two portals, a few articles are included that were written when the Russian troops were only getting ready on the border. 

After the war started, obviously there was a very high demand for latest news on the events and the number of articles in the days afterwards reachd higher than 80 articles a day. As time passed, however, the coverage on the events started to decrease though with high volatility, indicating that on days when some military operation is taking place, the number of articles still tend to increase significantly. 

After the designated events of 3rd April, there was a smaller spike reaching 40 articles a day, but in general, the number of articles became roughly constant at around 20 articles a day. 

```{r number of articles over time, include = FALSE}
#get number of articles and average length of articles by date
overtime <- tok_count %>%
  group_by(dates) %>% 
  summarise( 
    n_articles = n(),
    avg_tokens = mean(sum_tokens)
  )


#plot number of articles in dataset over time
arrows <- 
  tibble(
    x1 = c(ymd("2022-2-8"), ymd("2022-4-15")),
    x2 =  c(ymd("2022-2-24"),ymd("2022-4-3")),
    y1 = c(55, 45), 
    y2 = c(65, 48)
  )

ggplot(overtime, aes(dates, n_articles)) +
  geom_line() +
  labs(
    y = "Number of articles",
    x = NULL
  ) + 
  geom_vline(xintercept=ymd("2022-2-24"), linetype="dashed", 
             color = "red", size=1) + 
  geom_vline(xintercept=ymd("2022-4-3"), linetype="dashed", 
             color = "red", size=1) +
  ggplot2::annotate("text", x = ymd("2022-2-8"), y = 52, label = "Russian invasion of \n Ukraine") +
  ggplot2::annotate("text", x = ymd("2022-4-19"), y = 48, label = "Elections/\nBucha massacre") +
  geom_curve(
    data = arrows, aes(x = x1, y = y1, xend = x2, yend = y2),
    arrow = arrow(length = unit(0.08, "inch")), size = 0.5,
    color = "gray20", curvature = -0.3) +
  theme_adam()

ggsave("../images/count_over_time.png")

```

Then, I look at the length of articles as well (defined by the average number of tokens in the articles each day). As we can see, ery interestingly, the tendencies are exactly the opposite than that of the number of articles. After the invasion, the articles became longer and longer (there is of course volatility here as well, but still). Right before the elections, the average length of articles reached almost 800 tokens, which is roughly the double of the length of articles when the invasion happened. This is probably attributable to the fact that in the beginning, most of the articles were simple short descriptions of the (military) events. But later on, more analysis of the underlying reasons and consequences appeared on these portals that required longer pieces. Also with the elections approaching, such articles may be more effective in shaping the public's opinion on the matter. 

Then, after the elections, the length of the articles dropped to the level where it was when the war broke out (around 400). This may be due to lower interest due to the lack of relevance in domestic politics or the retrn of more shorter pieces on war events. 

```{r evolution of length of articles, include = FALSE}
#plot of evolution of length of articles
arrows <- 
  tibble(
    x1 = c(ymd("2022-2-3"), ymd("2022-4-23")),
    x2 =  c(ymd("2022-2-24"),ymd("2022-4-3")),
    y1 = c(650, 200), 
    y2 = c(700, 250)
  )

ggplot(overtime, aes(dates, avg_tokens)) +
  geom_line() +
  labs(
    y = "Average length of articles",
    x = NULL
  ) + 
  geom_vline(xintercept=ymd("2022-2-24"), linetype="dashed", 
             color = "red", size=1) + 
  geom_vline(xintercept=ymd("2022-4-3"), linetype="dashed", 
             color = "red", size=1) +
  ggplot2::annotate("text", x = ymd("2022-2-2"), y = 620, label = "Russian invasion of \n Ukraine") +
  ggplot2::annotate("text", x = ymd("2022-4-23"), y = 230, label = "Elections/\nBucha massacre") +
  geom_curve(
    data = arrows, aes(x = x1, y = y1, xend = x2, yend = y2),
    arrow = arrow(length = unit(0.08, "inch")), size = 0.5,
    color = "gray20", curvature = -0.3) +
  theme_adam()

ggsave("../images/length_over_time.png")

```

## Data cleaning

For the data cleaning part, I create a function that does all the necessary steps and can be applied to the raw texts in the dataset. First, it removes all the punctuations and numbers from the texts. This is necessary, because they do not contain any meaningful information for our type of analysis (even numbers, because as they are text in this context, the difference between 5 and 10 is the same as that of 5 and 11). Then, all text is made lower case so that words at the beginning and end of sentences are treated as the same tokens. Next, all whitespaces at the end of the documents and between words are removed. 

After tokenization, two sets of Hungarian stopwords are removed, one is provided by the [quanteda](https://quanteda.io) package and the other is specifically developed for political texts and was developed by a research group at the Hungarian Academy of Sciences: [link](https://github.com/poltextlab/HunMineR). Finally, I remove all tokens that consist of only 3 characters or less as they are most likely text garbage as well. 

After pasting the tokens back together, I assign the cleaned texts to a separate column of my dataframe. 

```{r data cleaning}
#load stopwords
custom_stopwords <- HunMineR::data_stopwords_extra

cleaner <- function(text) {
  
  #remove punctuations, numbers, make it lower case, remove unnecessary white spaces
  text <- stringr::str_remove_all(string = text, pattern = "[:punct:]") 
  text <- stringr::str_remove_all(string = text, pattern = "[:digit:]") 
  text <- stringr::str_to_lower(text)
  text <- stringr::str_trim(text) 
  text <- stringr::str_squish(text)
  
  # tokenize, filter out stopwords, drop those with less than 3 characters
  tokens <- unlist(strsplit(text, "\\s+"))
  tokens <- tokens[!(tokens %in% quanteda::stopwords("hungarian"))]
  tokens <- tokens[!(tokens %in% custom_stopwords)]
  tokens <- tokens[length(tokens) >= 3]
  
  # get back processed text
  clean_text <- paste0(tokens, collapse = " ")
  
  return(clean_text)
}

#apply function
df$clean_text <- pblapply(df$text, cleaner)
```


## Word frequencies

```{r word frequencies}
#create tidy tokens dataframe using tidytext from tokens before designated date
tokens_before <- df |> 
  filter(label == "before") |> 
  unnest_tokens(word, clean_text)

#count tokens by article
tok_count_before <- tokens_before |> 
  count(word, sort = TRUE) |> 
  top_n(10) |> 
  mutate(group = "before")

#create tidy tokens dataframe using tidytext
tokens_after <- df |> 
  filter(label == "after") |> 
  unnest_tokens(word, clean_text)

#count tokens by article
tok_count_after <- tokens_after |> 
  count(word, sort = TRUE) |> 
  top_n(10) |> 
  mutate(group = "after")

freq <- bind_rows(tok_count_after,tok_count_before)

#before after word frequency
freq %>% 
  ggplot(aes(x = tidytext::reorder_within(x=word, 
                                          by=n, 
                                          within=group), 
             y = n)) +
  geom_point() +
  coord_flip() +
  labs(x = NULL,
       y = "Frequency") +
  facet_wrap(~group, scales = "free") +
  tidytext::scale_x_reordered() +
  theme_adam()

ggsave("../images/word_freq.png")

```



```{r wordcloud}
#count tokens by article 2
tok_count_before2 <- tokens_before |> 
  count(word, sort = TRUE) |> 
  top_n(40) |> 
  mutate(group = "before")

#count tokens by article 2
tok_count_after2 <- tokens_after |> 
  count(word, sort = TRUE) |> 
  top_n(40) |> 
  mutate(group = "after")

freq2 <- bind_rows(tok_count_after2,tok_count_before2)

#wordcloud
freq2|> 
  ggplot(aes(label = word, size = n, colour = group)) +
  scale_size_area(max_size = 10) +
  geom_text_wordcloud(show.legend = TRUE) +
  theme_minimal()

ggsave("../images/wordcloud.png")
```






